\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{rotating}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{flafter}
%\usepackage{floatflt}
\usepackage{placeins}
\usepackage{siunitx}
\usepackage{graphicx}
\graphicspath{{./figures/}}% Include figure files
%\usepackage{epstopdf}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{cases}
\usepackage{calc}
\usepackage{amssymb}
\usepackage[dvips]{color}
\usepackage{color}
\usepackage{enumitem}
\usepackage{soul}
\usepackage{indentfirst}
\usepackage{hyphenat}
\usepackage{xspace}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{lineno}
\usepackage{setspace}
\newcommand{\tbxmulticol}[3]
    {\multicolumn{#1}
                 {>{\centering\hsize=\dimexpr#1\hsize+#1\tabcolsep+\arrayrulewidth\relax}#2}
                 {#3}}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
%\newcommand{\cmpersec}{$\frac{\text{cm}}{\text{s}}$~}
\newcommand{\cmpersec}{cm/s~}
\newcommand{\etal}{\textit{et al.}}
\newcommand{\na}{Na\textsuperscript{+}}
\newcommand{\cl}{Cl\textsuperscript{-}}
\newcommand{\PM}{$\pm$~}
\newcommand{\invnm}{$\text{\si{\nm}}^{-1}$~}
\newcommand{\nmeter}{\si{\nm}~}
\renewcommand{\arraystretch}{1.8}
\newcommand{\TODO}{\hl{TODO}~}
\newcommand{\about}{$\sim$}
\newcommand{\aangstroms}{{\aa}ngstr{\"o}ms}
\newcommand{\aangstrom}{{\aa}ngstr{\"o}m}
\newcommand{\sigmaij}{$\sigma_{ij}$}
\newcommand{\epsilonij}{$\epsilon_{ij}$}
\newcommand{\db}{$\text{D}_\text{B}$}
\newcommand{\dhh}{$\text{D}_\text{hh}$}
\newcommand{\dc}{$\text{2D}_\text{C}$}
\newcommand{\beginsupplemental}{%
    \setcounter{table}{0}
    \renewcommand{\thetable}{S\arabic{table}}%
    \setcounter{figure}{0}
    \renewcommand{\thefigure}{S\arabic{figure}}%
}
%\documentclass[10pt,p\begin{document}
\begin{document}
\section*{Reviewer 2}
\paragraph{Reviewer Comment 1:}
The revised manuscript is substantially improved;  the authors responded 
in a positive way to all the comments I made.  
The manuscript can be published now, but before the publication the 
authors should pay attention to the following issues:
Line 66: “strongly” used twice.
\paragraph{Response:}
The authors thank the reviewer for this note, it has been fixed in the manuscript.
\paragraph{Reviewer Comment 2:}
Lines 396-397: I do not understand what the authors mean by the sentence 
“This was found by fitting an exponential function to this region and taking the timescale 
from this fit as the boundary with bulk solvent”.  Something is wrong here.
\paragraph{Response:}
We agree with the reviewer, this was a mistake in the language. We have changed the word 'timescale' to 
'scale parameter' in this statement.
\paragraph{Reviewer Comment 3:}
Line 459: The value of D for the system with optimized parameters is twice 
the value for the system with LB parameters.  Does this make sense?
\paragraph{Response:}
The authors apologize for the lack of clarity in the manuscript. The value of D is measured as the distance
between the hydration boundaries of each leaflet of the bilayer, across the solvent-occupied region of the
simulation box. Since the system simulated with optimized parameters has twice as much solvent as the LB simulation, 
this larger distance across the solvent-occupied region is expected. We have added a statement elaborating on
this to the manuscript.

\end{document}
